\section{Conclusions and Acknowledgements}
\label{conclu}

In this paper several new algorithms were presented that make
multipole-accelerated three-dimensional capacitance calculation
applicable and computationally efficient for almost any geometry of
conductors in a homogeneous dielectric medium.  In particular, a new
adaptive multipole algorithm was described, along with a strategy for
accelerating iterative algorithm convergence by exploiting
electrostatic screening.  Results from using FASTCAP, our program
based on these techniques, to compute the capacitance of a wide range
of examples were given, and they demonstrated that the new algorithms
are nearly as accurate as the more standard direct factorization
approach, and are more than two orders of magnitude faster for large
examples. Current research in progress is in extending the above
approach to solving problems with piecewise-constant dielectrics and
ground planes.

The authors would like to thank Prof. Senturia for many valuable
discussions on various approaches to preconditioning, and for his and
Brian Johnson's help in linking FASTCAP with the M.I.T.  MEMCAD
system. The authors would also like to thank David Ling and Albert
Ruehli of the I.B.M.\ T.\ J.\ Watson Research Center for their helpful
suggestions about capacitance calculations.  In addition, we would
like to acknowledge the help of the members of the M.I.T.\ custom
integrated circuits group. Finally, we are indebted to several
anonymous reviewers for their careful evaluations of an earlier draft
of this paper.
