%\begin{thebibliography}{katzenelson88}
\begin{thebibliography}{[xx]} 

%\bibitem[dewilde90]{dew}
\bibitem{dew}
P.\ Dewilde and Z.-Q.\ Ning, {\em Models for Large Integrated Circuits},
Kluwer Academic Publishers, Boston, Massachusetts, 1990.

%\bibitem[golub83]{gol}
%G.\ Golub and C.\ Van Loan, {\em Matrix Computations},
%Johns Hopkins University Press, Baltimore, Maryland, 1983.

%\bibitem[greengard87]{gre} 
%L.\ Greengard and V.\ Rohklin, ``A Fast Algorithm for Particle Simulations,''
%J.\ Comp.\ Phys., vol.\ 73, pp.\ 325--348, 1987.

%\bibitem[greengard87]{gre}
\bibitem{gre}
L.\ Greengard, {\em The Rapid Evaluation of Potential Fields in Particle
Systems}, M.I.T.\ Press, Cambridge, Massachusetts, 1988.
%Yale University Research Report YALEU/DCS/RR-533, April 1987.

%\bibitem[greengard88]{fft} 
\bibitem{fft} 
L.\ Greengard and V.\ Rohklin, {\em On the Efficient Implementation of the Fast
Multipole Algorithm},
Yale University Research Report YALEU/DCS/RR-602, February 1988.

%\bibitem[guerrieri88]{gue}
\bibitem{gue}
R.\ Guerrieri and A.\ Sangiovanni-Vincentelli,
``Three-dimensional capacitance evaluation on a Connection Machine,''
{\em IEEE Trans.\ on Computer-Aided Design,} vol.\ CAD-7, no.\ 11, 
pp.\ 1125--1133, November 1988.

%\bibitem[harrington67]{har}
%R.\ F.\ Harrington, ``Matrix Methods for Field Problems,''
%{\em Proc.\ of the IEEE}, vol.\ 55, no.\ 2, pp.\ 136--149, February 1967.

%\bibitem[harrington68]{har}
\bibitem{har}
R.\ F.\ Harrington, {\em Field Computation by Moment Methods},
Macmillan, New York, 1968.

%\bibitem[hess66]{hes}
\bibitem{hes}
J.\ L.\ Hess and A.\ M.\ O.\ Smith, 
``Calculation of potential flow about arbitrary bodies,''
{\em Progress in Aerospace Sciences}, vol.\ 8, pp.\ 1--138, 1966.

%\bibitem[hobson55]{hob}
\bibitem{hob}
E.\ W.\ Hobson, {\em The Theory of Spherical and Ellipsoidal Harmonics},
Chelsea, New York, 1955.

%\bibitem[jackson75]{jac}
\bibitem{jac}
J.\ D.\ Jackson, {\em Classical Electrodynamics}, 
J.\ Wiley and Sons, New York, 1975.

%\bibitem[katzenelson88]{kat}
\bibitem{kat}
J.\ Katzenelson, {\em Computational Structure of the N-body Problem},
Mass.\ Inst.\ of Tech., Artificial Intelligence Laboratory, AI Memo 1042,
April 1988.

%\bibitem[lowan45]{low}
%\bibitem{low}
%A.\ N.\ Lowan, Director Mathematical Tables Project, 
%National Bureau of
%Standards, {\em Tables of Associated Legendre Functions}, Columbia University
%Press, New York, 1945, pg.\ xvii.

%\bibitem[magnus49]{mag}
\bibitem{mag}
W.\ Magnus and F.\ Oberhettinger, {\em Special Functions of Mathematical
Physics}, Chelsea, New York, 1949, pg.\ 54.

%\bibitem[ning88]{Nin}
\bibitem{Nin}
Z.-Q.\ Ning and P.\ M.\ Dewilde, ``SPIDER: capacitance modeling for VLSI 
interconnections,''
{\em IEEE Transactions on Computer-Aided Design}, vol.\ CAD-7, no.\ 12, 
pp.\ 1221--1228, December 1988.

%\bibitem[rao84]{rao}
\bibitem{rao}
S.\ Rao, T.\ Sarkar and R.\ Harrington, ``The Electrostatic Field of Conducting
Bodies in Multiple Dielectric Media,''
{\em IEEE Transactions on Microwave Theory and Techniques}, vol.\ MTT-32,
no.\ 11, pp.\ 1441--1448, November 1984.

%\bibitem[rohklin86]{roh}
\bibitem{roh}
V.\ Rohklin, ``Rapid Solution of Integral Equations of Classical Potential 
Theory,'' J.\ Comput.\ Phys., vol.\ 60, no.\ 2, pp.\ 187--207, 1985.

%\bibitem[ruehli73]{rue}
\bibitem{rue}
A.\ Ruehli and P.\ A.\ Brennen, ``Efficient capacitance calculations for 
three-dimensional multiconductor systems,''
{\em IEEE Transactions on Microwave Theory and Techniques}, vol.\ MTT-21,
no.\ 2, pp.\ 76--82, February 1973.

%\bibitem[saad86]{saa}
\bibitem{saa}
Y.\ Saad and M.\ H.\ Schultz,
``GMRES: A Generalized Minimal Residual Algorithm for Solving Nonsymmetric
Linear Systems,''
{\em SIAM J.\ Sci.\ Stat.\ Comput.}, vol.\ 7, no.\ 3, pp.\ 856--869, July 1986.

%\bibitem[zemanian89]{zem}
\bibitem{zem}
A.\ H.\ Zemanian, R.\ P.\ Tewarson, C.\ P.\ Ju, and J.\ F.\ Jen,
``Three-Dimensional Capacitance Computations for VLSI/ULSI Interconnections,''
{\em IEEE Trans.\ on Computer-Aided Design}, vol.\ CAD-8, no.\ 12, 
pp.\ 1319--1326, December 1989.

%\bibitem[zhao87]{zha}
\bibitem{zha}
F.\ Zhao, {\em An O(N) Algorithm for Three-Dimensional N-body Simulations},
Master's thesis, Mass.\ Inst.\ of Tech., Dept.\ of Elec.\ Eng.\ and 
Comp.\ Sci., October 1987.

\end{thebibliography}
