%\begin{singlespace}
\section{Solution by the Generalized Conjugate Residual Method}
%\end{singlespace}
\label{gcrsec}

In order to solve for a complete $ m\times m $ capacitance matrix, the
$ n\times n $ matrix of potential coefficients, $ P $, must be
factored once, usually into $ P = LU $, where $L$ and $U$ are
strictly lower and upper triangular respectively, and this requires order $
n^3 $ operations.  Then, as there are $ m $ conductors, the factored
system must solved $ m $ times with $ m $ different right-hand sides,
and this requires order $ m n^2 $ operations.  Since $ n $ is the
total number of panels into which the conductor surfaces are discretized, 
$ m $ is necessarily much smaller than $ n $.  Therefore, the $ n^3 $
time for 
factorization dominates for large problems, but factorization
can be avoided by
using iterative methods to solve the $ m $ charge distribution problems.

From the definition $ P $ given by   (\ref{eq:pcoeff}), it is clear
that $ P $ is a positive nonsymmetric matrix and that the largest
element in each row is the diagonal, though the matrix is {\it not }
diagonally dominant.  Therefore, conjugate-descent methods like the
generalized conjugate residual (GCR) algorithm  \cite{saa} given below
in Algorithm 1, are  likely to be more effective than the more familiar
Gauss-Seidel or Gauss-Jacobi style algorithms.
%\begin{table}
%\begin{singlespace}
\begin{tabbing}
{\bf Algorithm 1: GCR algorithm for solving $ Pq = p $}\\[0.2in]
T \= \kill
\>T \= \kill
\>\>T \= \kill
\>\>\>T \= \kill
\> /* The Setup. Note the $ u^{iter}$'s are search directions and */ \\
\> /* $ w $ is the residual. */\\
\> \> $w = p$; $q = 0$.\\
\> /* GCR Loop. */ \\
\> For $ iter = 0, 1, 2, ... $ until converged {\bf \{ }\\
\> \> $ u^{iter} = w $. \\
\> \> $ pu^{iter} = P w $.\\
\> \> /* P-orthogonalize $pu^{iter}$ with respect to $pu^m$, $ m < iter $. */\\
\> \> For $ m = 0 $ to  $ iter $ {\bf \{ }\\
\> \> \> $ \beta = pu^{iter\: T}pu^m $.\\
\> \> \> $ u^{iter} = u^{iter} - \beta u^m $.\\
\> \> \> $ pu^{iter} = pu^{iter} - \beta pu^m $.\\
\> \> {\bf \} }\\
\> \> /* Normalize the direction. */\\	
\> \> $ pu^{iter} = pu^{iter}/\|pu^{iter}\| $.\\
\> \> $ u^{iter} = u^{iter}/\|pu^{iter}\| $.\\
\> \> /* Update the charge and the residual. */	\\
\> \> $ \alpha = w^Tpu^{iter} $.\\
\> \> $ q = q + \alpha u^{iter} $.\\
\> \> $ w = w - \alpha pu^{iter} $.\\
\> {\bf \} }\\
\end{tabbing}
%\end{singlespace}
%\end{table}
